---
title: "Homework 1"
author: "Kehan Su ks4186"
date: 2024-09-21
output: github_document
---

```{r echo = FALSE, message = FALSE}
library(tidyverse)
```

## Problem 1


```{r data import}
data("penguins", package = "palmerpenguins")
view(penguins)
```

```{r info check}
nrow_penguins = nrow(penguins)
ncol_penguins = ncol(penguins)
mean_flipper_length = mean(pull(penguins, flipper_length_mm), na.rm = TRUE)

nrow_penguins
ncol_penguins
mean_flipper_length
```

data description:

The data includes the information of 344 penguins from 2007 to 2009.There are 8 variables: species, island, bill length, bill depth, flipper length, body mass, sex, and year.

The mean flipper length is 200.9152 mm.

```{r plot}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("flipper_vs_bill_scatterplot.png")
```


## Problem 2
```{r}
problem2_df = tibble (
  vec_number = rnorm(10),
  vec_logical = vec_number > 0,
  char_vec = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"),
  factor_vec = factor(c("level1","level1","level1","level2","level2","level2","level2","level3","level3","level3"))
)
view(problem2_df)
```

take mean value

```{r}
mean_number = mean(pull(problem2_df,vec_number))
mean_logical = mean(pull(problem2_df,vec_logical))
mean_character = mean(pull(problem2_df,char_vec))
mean_factor = mean(pull(problem2_df,factor_vec))
```
The former 2 work while the later 2 doesn't work

```{r}
numeric_number = as.numeric(pull(problem2_df,vec_number))
numeric_logical = as.numeric(pull(problem2_df,vec_logical))
numeric_character = as.numeric(pull(problem2_df,char_vec))
numeric_factor = as.numeric(pull(problem2_df,factor_vec))
```

Characters cannot be directly converted to numeric
Factors have underlying integer levels. When coerced to numeric, R converts the factors to these underlying integers (i.e., "A" becomes 1, "B" becomes 2, etc.). Therefore, taking the mean after coercion will give the mean of these numeric levels, but it may not have a meaningful interpretation.